Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2018-06-15 paper.tex
Update arxiv-only references to real journals, and update intro language

%\subsubsection*{Why ray tracing?}
Angular and spectral neutrino distributions in neutron star merger simulations may
be available soon, for example with the coupled Monte-Carlo-M1 scheme presented in
\citep{fouc2017-m1_with_mc}.
In this work, however, we present a ray tracing method to compute neutrino
distribution functions from the existing state-of-the-art general relativistic M1
transport hydrodynamics simulations.
We choose ray tracing because it is conceptually simple,
numerically inexpensive,
and extends to high resolution in energy and angle
by simply increasing the number of rays sampled.
Furthermore, the computational implementation parallellizes trivially.

>>>>

%\subsubsection*{Why ray tracing?}
Angular and spectral neutrino distributions in neutron star merger simulations
have just recently become available with a coupled Monte-Carlo-M1 scheme
\citep{fouc2017-m1_with_mc,fouc2018-mc_for_errors}.
In this work, however, we present a ray tracing method to compute neutrino
distribution functions from the more widely available state-of-the-art
general relativistic M1 transport hydrodynamics simulations.
We choose ray tracing because it is conceptually simple,
numerically inexpensive,
and extends to high resolution in energy and angle
by simply increasing the number of rays sampled.
Furthermore, the computational implementation parallellizes trivially.
